Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/4.ProgammingModel.tex
Removed subsection-headline.
Bug fix.

\subsection{Kokkos Abstractions}

@@

Figure~\ref{fig:parallelFor} shows one definition of the Kokkos~\emph{parallel\_for} interface. This interface accepts two template parameters and three function arguments. \emph{ExecPolicy} shapes the iteration space for a particular execution space. Valid template parameter are the~\emph{RangePolicy},~\emph{TeamPolicy},~\emph{MDRangePolicy},~\emph{TeamThreadRange} and~\{ThreadVectorRange}. As the name suggests, these policies express how an iteration space is mapped to the underlying hardware. For example, a range policy defines a one dimensional iteration range. A team policy defines a 1D iteration range, each of which is assigned to a thread team. This policy allows the expression of hierarchical parallelism. The second template parameter,~\emph{FuntorType}, represent a functor that implements the~\{()-operator} with a matching signature for the given execution policy. The functor can be defined using a C++ class, struct or lambda expression. We show an example of how a parallel for loop is expressed and mapping to the vendor-specific back-end in the next chapter. For the interested reader, the complete programming model specification can be accessed on-line\cite{pub:KOKKOS}. Figure~\ref{fig:abstractions} lists patterns and abstractions and structures them by information type in the semantic capture.

>>>>

@@

Figure~\ref{fig:parallelFor} shows one definition of the Kokkos~\emph{parallel\_for} interface. This interface accepts two template parameters and three function arguments. \emph{ExecPolicy} shapes the iteration space for a particular execution space. Valid template parameter are the~\emph{RangePolicy},~\emph{TeamPolicy},~\emph{MDRangePolicy},~\emph{TeamThreadRange} and~\emph{ThreadVectorRange}. As the name suggests, these policies express how an iteration space is mapped to the underlying hardware. For example, a range policy defines a one dimensional iteration range. A team policy defines a 1D iteration range, each of which is assigned to a thread team. This policy allows the expression of hierarchical parallelism. The second template parameter,~\emph{FuntorType}, represent a functor that implements the~\emph{()-operator} with a matching signature for the given execution policy. The functor can be defined using a C++ class, struct or lambda expression. We show an example of how a parallel for loop is expressed and mapping to the vendor-specific back-end in the next chapter. For the interested reader, the complete programming model specification can be accessed on-line\cite{pub:KOKKOS}. Figure~\ref{fig:abstractions} lists patterns and abstractions and structures them by information type in the semantic capture.
